### 2020-03-08 draft_ABP.tex
Update draft_ABP.tex

\usepackage{comment}
\input epsf.sty
\topmargin -.1cm
\textheight 21cm
\oddsidemargin 0.15cm 
\textwidth 14cm
\usepackage{cite}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx,paralist}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
\usepackage[skip=10pt]{caption} % example skip set to 2pt
\usepackage{comment}

@@

Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
they satisfy the so called $u$-equations with the form
\begin{equation}\label{perfectu}
	1-u_i=\prod_{j}u_j^{(i||j)},
\end{equation}
where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
Varieties defined by $u$-equations associated with finite type clusters 
are called cluster configuration spaces. 
For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
Therefore, these $u$-equations reveal the binary structure of the cluster
configuration spaces.

For example, $A_n$ type cluster configuration spaces come from original string 
amplitudes
\[
	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n}
	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
	\prod_{i<j} (z_j-z_i)^{\alpha' s_{ij}},
\]
where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
It's not in the form of stringy integrals, but we can use a positive
parametrization 
\[
z_3=1+x_2,\quad z_4=1+x_2+x_3,\quad \dots, \quad 
z_{n-1}=1+x_2+\cdots+x_{n-2}
\]
to rewrite the integral $\mathcal I_n$, then
\[
    \mathcal I_n=\int_{\mathbb R_+^{n-3}}
	\frac{\mathrm dx_2\cdots \mathrm dx_{n-2}}{x_2\cdots x_{n-2}}
	\prod_{i<j} p_{ij}^{\alpha' s_{ij}},
\]
where $p_{ij}=x_i+\cdots+x_{j-1}$. The $u$-variables of this configuration space are
\[
	u_{ij}=\frac{p_{i-1,j}p_{i,j-1}}{p_{ij}p_{i-1,j-1}},
\]
and they satisfy the $u$-equations
\[
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
\]
where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
$(n+3)$-gon are crossed.

Another example still comes from a hyperplane arrangement, the Shi arrangement,
which is also $B_n$ type cluster stringy integral.
The Shi arrangement contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom of global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
given by the following hyperplains
\[
    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
\]
for $1\leq i<j\leq n+1$. Its stringy integral is
\[
	\mathcal I_n = \int_{z_1<z_2<\cdots <z_n<0}
	\frac{\mathrm dz_1\cdots \mathrm dz_{n}}{(z_1-z_2)\cdots (z_{n}-z_{n+1})}
    \prod_{1\leq i<j \leq n}(z_j-z_i)^{s_{ij}}|z_i-z_j-1|^{t_{ij}}
\]
(Zhenjie: Carefully check the notation!)
The $u$-variables of this configuration space are
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.

@@

\newpage
\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon $P_n$ are binary geometries. Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}
******************************************************************************************
\section*{Permutahedron}
 For $x_1,x_2, \cdots, x_{n+1} \in \mathbb{R} $ , the permutahedron ${\mathscr P_n}(x_1,\cdots,x_{n+1})$ is a convex polytope in $\mathbb{R}^{n+1}$ defined as the convex hull of all vectors obtained from $(x_1,x_2, \cdots, x_{n+1})$ by permutations of the coordinates:
 \bea
{\mathscr P_n}(x_1,x_2, \cdots, x_{n+1}) = {\rm ConvexHull} \{ (x_{w(1)},x_{w(2)}, \cdots, x_{w(n+1)})~ |~ w \in S_{n+1} \}, \nonumber
 \eea
 where $S_{n+1}$ is the symmetric group.

 The permutahedron has $(n+1)!$ vertices and is of dimension at most $n$ since it lies in the hyperplane 
 \bea
 H_c= \{(t_1,t_2, \cdots, t_{n+1}) | t_1 + t_2 + \cdots + t_{n+1}= c \} \subset \mathbb{R}^{n+1}, \nonumber
 \eea
where $c= x_1+x_2+ \cdots +x_{n+1}$.

For $n=1$ and distinct $x_1,x_2$ the permutahedron ${\mathscr P_1}(x_1,x_2)$ is a line. If  $x_1=x_2$ then it degenerates into a single point.

For $n=2$ and distinct $x_1,x_2, x_3$ the permutahedron ${\mathscr P_2}(x_1,x_2, x_3)$ is a hexagon. If two of the $x_i$'s are equal then the permutahedron degenerates into a triangle and if $x_1= x_2 = x_3$ then its degenerates into a single point.

We shall list a few results about permutahedra which shall be useful for later purposes: 
\begin{itemize}
\item {\bf Coordinate independence:} The combinatorial structure of the permutahedron ${\mathscr P_n} (x_1, \cdots, x_{n+1}) $ does not depend on $ x_1, \cdots, x_{n+1} $ as long as all these are distinct. Henceforth  we will choose $ \{x_1, \cdots, x_{n+1}\} = \{0,1,\cdots,n \} := [0,n ]$. \\
\item {\bf Facial Structure:} The $(n-k)$ faces of ${\mathscr P_n}$ are in an $1-1$ correspondence with the decomposition of $[0,n]$ into $k$ parts. More precisely, for each $(S_1,\cdots,S_k)$ with $S_i \neq \emptyset ~ \forall i$ and $[0,n] = S_1 \sqcup \cdots \sqcup S_k$ the corresponding face $\pi_{S_1,\cdots,S_k}$ has vertices which are permutations such that the entries $ \{x_i | i \in S_1 \}$ are largest $|S_1|$ numbers in $[0,n]$, $\{x_i | i \in S_2 \}$ are largest $|S_2|$ numbers in $[0,n]$ and so on.

Further the face $\pi_{S_1,\cdots,S_k}$   is isomorphic to ${\mathscr P_{\left(| S_1|-1\right)} }\times {\mathscr P_{\left(| S_2|-1\right)} } \cdots \times{\mathscr P_{\left(| S_k|-1\right)} } $.

It follows from above that ${\mathscr P_n}$ has $2^{n+1} -2$ facets corresponding to all the non-empty proper subsets of $I$ for which we have a decomposition $[0,n] = S \sqcup S^c$ and the facets are isomorphic to one of the following product of lower dimensional permutahedra  $ \{ {\mathscr P_{n-1}}, {\mathscr P_{n-2}} \times A_1, \cdots ,{\mathscr P_{\lfloor{n/2 \rfloor}}} \times {\mathscr P_{n-1-\lfloor n/2 \rfloor}}  \} $\footnote {More generally the number of $(n-k)$ facets of ${\mathscr P_n}$ is $ k! S(n,k)$ where $S(n,k)$ is the Stirling number of the second kind which counts the number $k$ partitions of  $I$ and there are $p(n+1,k)$ types where $p(n+1,k)$ is the number of $k$ partitions of $(n+1)$.}.

It also follows from above that a face $\pi_{S_1,\cdots,S_k}$ is contained in another face $\pi_{T_1,\cdots,T_l}$ if and only if each $T_i$ is a union of consecutive $S_j$ or equivalently if $(S_1,\cdots,S_k)$ is a refinement of $(T_1,\cdots,T_l)$.
\item {\bf Minkowski decomposition:}   Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_{n+1})$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull}(e_i~|~i\in I)$ denote the face of the $\Delta_{[0,n]}$. The polytope $P_n(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I > 0$ for all nonempty subsets $I \subset [n+1]$
 \bea
 P_n(\{y_I \})= \sum_{I \subset[n+1]} y_I . \Delta_I  \nonumber
 \eea
 is the permutahedron ${\mathscr P_n}$
\end{itemize}
We shall now talk about generalized permutahedra which are polytopes obtained by deformations of the usual permutahedron i.e., obtained by moving the vertices of the usual permutahedron so that the directions of all the edges are preserved though some of the edges may degenerate into points.

\subsection*{Generalized permutahedra}

A  generalised permutahedron is obtained by parallel translation of facets of the usual permutahedron it is parametrized  by a collection $\{ z_I\}$ of $2^{n+1}-1$ coordinates, for non-empty sets of $I \subset [0,n] $
 \bea
 P_n^z(\{ z_I \}) = \left \{ (t_0 , t_2, \cdots , t_{n}) \in \mathbb{R}^{n+1} | \sum_{i=0}^{n} t_i = z_{[0,n]},~ \sum_{i \in I} t_i \geq z_I, {\rm for ~subsets} ~I  \right  \} \nonumber
 \eea
 (a better notation for generalized permutahedron ??)

 If $z_I =z_J$ whenever $|I| =|J|$, then  $ P_n^z(\{ z_I \})$ is the usual permutahedron. 
 \begin{itemize}
 \item The combinatorial structure of the generalised permutahedron depends only on the set $B$ of nonemepty subsets $I \subset [0,n]$ such that $y_I \geq 0$ which is called the {\it building set}. To describe the combinatorial structure we need the notion of {\it Nested complex} which we shall define now.
 \end{itemize}

\subsection*{Nested Complex}
If $B$ additionally satisfies the following:
\begin{compactenum}[\quad (1)]
    \item If $I,J \in B$ and $I \cap J \neq \phi $, then $I \cup J \in B$.
    \item $B$ contains all singletons $\{ i\}$ for $i \in S$.
\end{compactenum}

A subset $N$ in the building set $B$ is called a {\it nested set} if it satisfies the following conditions:
\begin{compactenum}[\quad (1)]
    \item For any $I,J \in N$, we either have $I \subset J$ or $J\subset I$ or $I$ and $J$ are disjoint.
    \item For any collection of $k \geq 2$ disjoint subsets $J_1,J_2,\cdots, J_k \in N$ their union $J_1 \cup \cdots \cup J_k$ is not in B.
    \item $N$ contains all maximal elements of $B$.
\end{compactenum}

 \begin{itemize}
\item {\bf Minkowski decomposition:} Let, $\Delta_{[0,n]} = {\rm ConvexHull}(e_1,\cdots,e_n)$ be the standard coordinate simplex in $\mathbb{R}^{n+1}$. For any $I \subset [0,n] $ let $\Delta_I ={\rm ConvexHull(e_i~|~i\in I)}$ denote the face of the $\Delta_{[0,n]}$. The polytope $P_n^y(\{y_I \})$ obtained as the Minkowski sum of simplices $\Delta_I$ scaled by  parameters $y_I \geq 0$ for all nonempty subsets $I \subset [0,n]$
 \bea
 P_n^y(\{y_I \})= \sum_{I \subset[0,n]} y_I . \Delta_I  \nonumber
 \eea
is the generalised permutahedron $P_n^z(\{z_I \})$ if $z_I = \sum_{J \subset I} y_J  ~{\rm for~all~nonempty} I \subset [0,n]$.
\footnote{Not all generalised permutahedra cannot be written as Minkowski sum of coordinate simplices. We shall restrict ourselves to the large class of generalised permutahedra which admit such a realisation.}

\item {\bf Facial structure:} Let us assume that the set $B$ associated with a generalised permutahedron $P_n^{y}$ is a building set on $[0,n]$. Then the poset of faces $P_n^{y}$ ordered by reverse inclusion is isomorphic to the nested complex $\mathcal{N}(B)$.

For each decomposition $[0,n]=  \sqcup_{I \subset N } S_I $ where $S_I$ are non-empty, the face $P_N$ of $P_n^{y}(y_I)$ associated with the nested set $N \in \mathcal{N}(B)$ is:
\bea
P_N = \sum_{{J \subset B}\atop{J \cap S_I \neq \emptyset}} y_{J} \Delta_{J \cap S_I}
\eea
\end{itemize}
In summary the above results imply that we can look at any collection of subsets of $[0, n]$ which form a building set $B$ and associate  coordinate simplex $\Delta_I$ for each $I \in B$ and resulting Minkowski sum with positive weights $y_I$ generates a generalised permutahedron associated with the building set. Further, the number of facets of the generalised permutahedron just correspond to the set of all non-singlet elements in $B$.

We shall set $x_0 =1$ from now on. Since, the number of singlets correspond to the dimension of the generalised permutahedron this implies that:

Thus, generalised permutahedra have ``Big Polytopes" which are simplices and we can write down the stringy canonical forms and solve for the $u$-variables and examine if they satisfy some kind of $u$-equations. We shall do this in subsequent sections (see section(2.2)).

(3) If $B$ corresponds to all the non empty subsets of $[0,n]$ and $Y_I =y_{|I|}$ i.e., the variables $Y_I$ are equal for all subsets of the same cardinality, then $P_n({\bf Y})$ is the usual permutahedron $P_n$.

(4)If $B=\{ [i,j] | 1\leq  i \leq j \leq n\}$ is the set of consecutive intervals, then $P_n({\bf Y})$ is the associahedron.

(5) If $B=\{ [1,i] \cup [j,n] | 1\leq  i \leq j \leq n\}$ is the set of cyclic intervals, then $P_n({\bf Y})$ is the Cyclohedron.

The cases (4) and (5) will be considered in section (3.2). In this section we shall restrict ourselves to the permutahedron example ${\mathscr P_n}$.  
\subsection{Natural stringy integrals with linear factors}

@@

>>>>

\usepackage{comment}
\input epsf.sty
\topmargin -.1cm
\textheight 21cm
\oddsidemargin 0.15cm 
\textwidth 14cm
\usepackage{cite}
\usepackage{epsfig,amssymb,euscript,xspace,xcolor}
\usepackage{amsmath,mathtools,empheq,amsthm,hyperref,graphicx}
\usepackage{mathrsfs,float}  
\usepackage{pgf,tikz,pgfplots}
\usetikzlibrary{arrows}
\usepackage[T1]{fontenc} 
\usepackage{tikz,caption,subcaption,marvosym} 
\usetikzlibrary{decorations.markings,arrows,snakes}
\usepackage[belowskip=-15pt,aboveskip=0pt]{caption}
\usepackage[skip=10pt]{caption} % example skip set to 2pt
\usepackage{comment}

@@

Generally, the big polyhdron of a stringy integral is not necessary to be a simplex.
It's known that stringy integrals associated to the $A_n$, $B_n$, $C_n$, $D_n$,
$E_6$, $E_7$, $E_8$, $F_2$ and $G_4$ type clusters are in this type. What's more,
they satisfy the so called $u$-equations with the form
\begin{equation}\label{perfectu}
	1-u_i=\prod_{j}u_j^{(i||j)},
\end{equation}
where $(i||j)\geq 0$ is a integral defined in the cluster algebra context \cite{}.
Varieties defined by $u$-equations associated with finite type clusters 
are called cluster configuration spaces. 
For this type equations, once $u_i$ goes to $0$, it forces some $u_j$ to go to $1$.
Therefore, these $u$-equations reveal the binary structure of the cluster
configuration spaces. ...

($A_n$ (sting integral?), $B_n$ (Shi arrangement?), or both from $F$-polynomial)

For example, $A_n$ type cluster configuration spaces come from original string 
amplitudes
\[
	\int_{z_1<z_2<\cdots <z_n}
	\frac{\mathrm dz_2\cdots \mathrm dz_{n-2}}{(z_1-z_2)\cdots (z_{n-2}-z_{n-1})}
	\prod_{i<j} (z_i-z_j)^{\alpha' s_{ij}},
\]
where we fix the gauge by setting $z_1=0$, $z_{n-1}=1$ and $z_n=\infty$.
The $u$-variables of this configuration space are
\[
	u_{ij}=\frac{(z_{i-1}-z_j)(z_i-z_{j-1})}{(z_i-z_j)(z_{i-1}-z_{j-1})},
\]
and they satisfy the $u$-equations
\[
	1-u_{ij}=\prod_{(k,l)\not\sim (i,j)}u_{kl},
\]
where $(i,j)\not\sim (k,l)$ means that diagonals $(i,j)$ and $(k,l)$ of
$(n+3)$-gon are crossed.

(Zhenjie: we should use another parametrization of $A_n$) 
(mention hyperplane arrangement)

$B_n$: Shi arrangement

The Shi arrangement of $B_n$ contains $n+1$ punctures $\{z_i\}_{i=1,\dots,n+1}$ 
on the real line with the freedom corresponding to the global transformation 
$z_i\to z_i+a$, so we can use it to fix $z_{n+1}=0$. Then the Shi arrangement is 
given by the following hyperplains
\[
    z_i-z_j=0\quad \text{and}\quad z_i-z_j=1,
\]
for $1\leq i<j\leq n+1$.

The the $u$ variables of $B_n$ can be solved by these $z_i$ by 
\[
    u_1=1+z_1-z_2,\quad \dots,\quad u_{n}=1+z_{n}-z_{n+1},\quad u_{n+1}=z_{n+1}-z_1
\]
and 
\[
\begin{aligned}
    u_{ji}&=\frac{(z_{j+1}-z_{i})(z_{i+1}-z_j)}{(z_{j+1}-z_{i+1})(z_i-z_j)}\quad &&\text{for $i<j$},\\
    u_{ij}&=\frac{(\tilde z_{j+1}-z_{i})(\tilde z_{i+1}-z_j)}{(\tilde z_{j+1}-z_{i+1})(\tilde z_i-z_j)}\quad &&\text{for $i<j$},
\end{aligned}
\]
where $\tilde{z}_i=z_{i+n+1}=z_{i}+1$ and indices are living in $\mathbb Z_{2n+2}$.

@@

\newpage
\section{Stringy canonical forms and $u$-equations for generalized permutahedra}
In this section we shall argue that  a large subset of generalised permutahedra which are realised as degenerations of permutahderon $P_n$ are binary geometries. Before we proceed we shall review some details about the generalised permutahedra which we shall use throughout the paper.
\subsection{Generalized permutohedra} {\bf the definition, facets and combinatorial factorizations, do $P_n$ example in full details.}

\subsection{Natural stringy integrals with linear factors}

@@

(Chi: I have checked several examples of graph associahedra, there is a conjecture for $u$ variables for this kind of generalized permutohedra: \\
For a element $I$ in the building set $\mathcal{B}$, we define $I_{\text{max}}=\Bigl(\bigcup_{j\sim I} \{j\} \Bigr)\cup I$
where $j\sim I$ means the singleton $j$ is attached to $I$ in the corresponding graph, then 
\begin{equation}
   u_{I} = \prod_{ I \subset J \subset I_{\text{max}}}x_J^{(-1)^{|I|-|J|}}.
\end{equation}
This conjecture can easily be extended to generalized permutohedra, but I only have checked the several cases of graph associahedra for now.
)

\subsubsection{Example: Binary geometries for Cayley graph, graph associahedra and generalized permutohedra. }

In the above, we have shown that the binary geometries exist for permutohedra even through the $u$ equtions are not perfect and conjecture that such binary geometries exist for generalized permutohedra. In the remainder of this section, we will give more example on such binary geometries without perfect $u$ equtions.

We start with the Cayley graph proposed in \cite{} and further studied in \cite{}. In \cite{}, the ABHY realization for general Cayley graphs have been proposed, here we will use several examples to illustrate that the binary geometries exist for general Cayley graphs. The first Cayley graph which is nether associahedron nor permutahderon is so-called  ``next-to-$A_{3}$'', in terms of generalized permutahdera, the building set for next-to-$A_{3}$ is 
\begin{equation}
   \mathscr{NA}_{3}=\{\{1,2,3,4\},\{1,2,3\},\{1,3,4\},\{2,3,4\},\{1,2\},\{1,3\},\{2,3\},\{3,4\},\{1\},\{2\},\{3\},\{4\}\}
\end{equation}

the $u$ variables are 
\begin{align}
   &u_{1}=\frac{x_{1}x_{123}}{x_{12}x_{13}} \:, \quad  u_{2}=\frac{x_{2}x_{123}}{x_{12}x_{23}} \:,  \quad 
   u_{3}=\frac{x_{3}x_{134}x_{234}x_{123}}{x_{34}x_{13}x_{23}x_{1234}} \:, \quad 
   u_{4}=\frac{x_{4}}{x_{34}} \\
   &u_{12}=\frac{x_{12}}{x_{123}} \:, \quad u_{13}=\frac{x_{13}x_{1234}}{x_{134}x_{123}} \:,\quad 
   u_{23}=\frac{x_{23}x_{1234}}{x_{123}x_{234}} \:, \quad u_{34}=\frac{x_{34}x_{1234}}{x_{134}x_{234}} \\
   &u_{123}=\frac{x_{123}}{x_{1234}} \:, \quad u_{134}=\frac{x_{134}}{x_{1234}} \:, \quad 
   u_{234}=\frac{x_{234}}{x_{1234}}
\end{align}
The $u$ equations are
\begin{align}
   &1-u_{1}=u_{2}u_{3}u_{23}^{2}u_{34}u_{234}^{2} \:, \\
   &1-u_{2}=u_{1}u_{3}u_{13}^{2}u_{34}u_{123}^{2} \:, \\
   &1-u_{3}= u_{1}u_{2}u_{4}u_{12}^{2}(1+u_{3}u_{13}u_{23}u_{34}u_{123}u_{134}u_{234}) \:, \\
   &1-u_{4}=u_{3}u_{13}u_{23}u_{123}  \:, \\
   &1-u_{12} =u_{3}u_{13}u_{23}u_{34}u_{134}u_{234} \:, \\
   &1-u_{13} =u_{2}u_{4}u_{12}u_{23}u_{34}u_{234}^{2} \:, \\
   &1-u_{23}= u_{1}u_{4}u_{12}u_{13}u_{34}u_{134}^{2} \:, \\
   &1-u_{34}= u_{1}u_{2}u_{12}^{2}u_{13}u_{23}u_{123}^{2} \:, \\
   &1-u_{123}=u_{4}u_{34}u_{134}u_{234} \:, \\
   &1-u_{134}=u_{2}u_{12}u_{23}u_{123}u_{234} \:, \\
   &1-u_{234}=u_{1}u_{12}u_{13}u_{123}u_{134} \:, 
\end{align}
